Solar wind discontinuities spatial evolution in the outer heliosphere

### 2024-02-06 _manuscript/_tex/article.tex
Built site for gh-pages

@@

@@

\includegraphics{figures/juno_orbit_white.pdf}

\caption{\label{fig-orbit}Juno orbit}

@@

\begin{minipage}{0.25\linewidth}
\includegraphics{figures/examples/artemis_id_example.pdf}\end{minipage}%
%
\begin{minipage}{0.25\linewidth}
\includegraphics{figures/examples/stereo_id_example.pdf}\end{minipage}%
%
\begin{minipage}{0.25\linewidth}
\includegraphics{figures/examples/wind_id_example.pdf}\end{minipage}%
%
\begin{minipage}{0.25\linewidth}
Examples of IDs from ARTEMIS, STEREO, and Wind\end{minipage}%

>>>>

\begin{minipage}{\linewidth}
\includegraphics{figures/juno_orbit_white.pdf}\end{minipage}%
\newline
\begin{minipage}{\linewidth}
\includegraphics{figures/juno-hg-loc_sunspot-number.pdf}\end{minipage}%

\caption{\label{fig-overview}Juno orbit, its longitudinal difference with Earth \& STEREO missions and sunspot number during its cruise phase}

@@

\section{Acknowledgements}\label{acknowledgements}

Sunspot data from the World Data Center SILSO, Royal Observatory of Belgium, Brussels

@@

@@

\begin{minipage}{\linewidth}
\includegraphics{figures/examples/artemis_id_example.pdf}\end{minipage}%
\newline
\begin{minipage}{\linewidth}
\includegraphics{figures/examples/stereo_id_example.pdf}\end{minipage}%
\newline
\begin{minipage}{\linewidth}
\includegraphics{figures/examples/wind_id_example.pdf}\end{minipage}%
\newline
\begin{minipage}{\linewidth}
Examples of IDs from ARTEMIS, STEREO, and Wind\end{minipage}%
